\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2020-04-09 analysis/paper/paper.Rmd
Uses development version of Jesse-Islam/riskRegression
It seems to be working with my version of riskRegression, with the function acting as a part of the package.

The issue with 1- absolute risk I was worried about is not longer an issue. Turns out It was wrong before anyway. predictRisk attempts to output the probability of the event occuring

predictRisk.singleRisk <- function(object, newdata, times, cause, ...) {
  if (object$call[[1]]!="glm"){
    #get all covariates excluding intercept and time
    coVars=colnames(object$originalData$x)
    #coVars is used in lines 44 and 50
    newdata=data.matrix(drop(subset(newdata, select=coVars)))
  }

  # if (missing(cause)) stop("Argument cause should be the event type for which we predict the absolute risk.")
  # the output of absoluteRisk is an array with dimension dependening on the length of the requested times:
  # case 1: the number of time points is 1
  #         dim(array) =  (length(time), NROW(newdata), number of causes in the data)
  if (length(times) == 1) {
    a <- absoluteRisk(object, newdata = newdata, time = times)
    p <- matrix(a, ncol = 1)
  } else {
    # case 2 a) zero is included in the number of time points
    if (0 %in% times) {
      # dim(array) =  (length(time)+1, NROW(newdata)+1, number of causes in the data)
      a <- absoluteRisk(object, newdata = newdata, time = times)
      p <- t(a)
    } else {
      # case 2 b) zero is not included in the number of time points (but the absoluteRisk function adds it)
      a <- absoluteRisk(object, newdata = newdata, time = times)
      ### we need to invert the plot because, by default, we get cumulative incidence
      #a[, -c(1)] <- 1 - a[, -c(1)]
      ### we remove time 0 for everyone, and remove the time column
      a <- a[-c(1), -c(1)] ### a[-c(1), ] to keep times column, but remove time 0 probabilities
      # now we transpose the matrix because in riskRegression we work with number of
      # observations in rows and time points in columns
      p <- t(a)
    }
  }
  if (NROW(p) != NROW(newdata) || NCOL(p) != length(times)) {
    stop(paste("\nPrediction matrix has wrong dimensions:\nRequested newdata x times: ", NROW(newdata), " x ", length(times), "\nProvided prediction matrix: ", NROW(p), " x ", NCOL(p), "\n\n", sep = ""))
  }
  p
}

class(cbFull) <- c("singleRisk",class(cbFull))
brierFinalResults <- Score(list("Cox" = coxFull,"Penalized Cox"=coxNet,"Penalized Logistic"=cbFull), data = test, formula = Hist(time, event != 0) ~ 1, summary = "ipa", se.fit = 0L, metrics = "brier", contrasts = FALSE, times =times)

@@

```{r coefplots,echo=FALSE, eval=eval_cs3}

@@

lolliplotDots <- rbind(estimatescb, estimatescoxNet, estimatescoxFull)
lolliplotDots$conf.low <- lolliplotDots$estimate
lolliplotDots$conf.high <- lolliplotDots$estimate
lolliplotDots$conf.high[lolliplotDots$estimate < 0] <- 0
lolliplotDots$conf.low[lolliplotDots$estimate > 0] <- 0
lolliplotDots$term=gsub( '\`', "", as.character(lolliplotDots$term))
dwplot(lolliplotDots)+
  theme(axis.text.y = element_text(size = 7.5, angle = 0, hjust = 1, vjust = 0),
        strip.text.x = element_blank(),
      strip.background = element_rect(colour="white", fill="white"),
      legend.position=c(.855,0.15),legend.text=element_text(size=7.5)
      )
```

>>>>

class(cbFull) <- c("singleEventCB",class(cbFull))
brierFinalResults <- Score(list("Cox" = coxFull,"Penalized Cox"=coxNet,"Penalized Logistic"=cbFull), data = test, formula = Hist(time, event != 0) ~ 1, summary = "ibs", se.fit = 0L, metrics = "brier", contrasts = FALSE, times =times)

@@

```{r coefplots,echo=FALSE, eval=eval_cs3, fig.cap="\\label{fig:cs3FinalBrier} A lollipop plot demonstrating the estimated coefficients between the following three models: Cox (blue), penalized Cox (Green), penalized logisitic (red). If a coefficient is estimated to be 0, it is removed from the plot"}

@@

lolliplotDots <- rbind(estimatescb, estimatescoxNet, estimatescoxFull)
lolliplotDots$conf.low <- lolliplotDots$estimate
lolliplotDots$conf.high <- lolliplotDots$estimate
lolliplotDots$conf.high[lolliplotDots$estimate < 0] <- 0
lolliplotDots$conf.low[lolliplotDots$estimate > 0] <- 0
lolliplotDots$term=gsub( '\`', "", as.character(lolliplotDots$term))

lolliplotDots[which(lolliplotDots$estimate==0),c(2,4,5)]<-NA

dwplot(lolliplotDots)+
  theme(axis.text.y = element_text(size = 7.5, angle = 0, hjust = 1, vjust = 0),
        strip.text.x = element_blank(),
      strip.background = element_rect(colour="white", fill="white"),
      legend.position=c(.855,0.15),legend.text=element_text(size=7.5)
      )
```

### 2020-04-09 analysis/paper/paper.tex
Uses development version of Jesse-Islam/riskRegression
It seems to be working with my version of riskRegression, with the function acting as a part of the package.

The issue with 1- absolute risk I was worried about is not longer an issue. Turns out It was wrong before anyway. predictRisk attempts to output the probability of the event occuring

\begin{center}\includegraphics{../figures/coefplots-1} \end{center}

\end{CodeChunk}

@@

This report was generated on 2020-03-31 18:19:20 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 3.6.1 (2019-07-05)
#> Platform: x86_64-w64-mingw32/x64 (64-bit)
#> Running under: Windows 10 x64 (build 18363)
#> 
#> Matrix products: default
#> 
#> locale:
#> [1] LC_COLLATE=English_United States.1252 
#> [2] LC_CTYPE=English_United States.1252   
#> [3] LC_MONETARY=English_United States.1252
#> [4] LC_NUMERIC=C                          
#> [5] LC_TIME=English_United States.1252    
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.5.5               dotwhisker_0.5.0         
#>  [3] prodlim_2019.11.13        riskRegression_2020.02.05
#>  [5] pracma_2.2.9              kableExtra_1.1.0         
#>  [7] data.table_1.12.8         glmnet_3.0-2             
#>  [9] Matrix_1.2-17             casebase_0.2.1.9001      
#> [11] survival_3.1-8            magrittr_1.5             
#> [13] forcats_0.5.0             stringr_1.4.0            
#> [15] dplyr_0.8.3               purrr_0.3.3              
#> [17] readr_1.3.1               tidyr_1.0.2              
#> [19] tibble_2.1.3              ggplot2_3.3.0            
#> [21] tidyverse_1.3.0          
#> 
#> loaded via a namespace (and not attached):
#>  [1] nlme_3.1-140        fs_1.3.2            cmprsk_2.2-9       
#>  [4] lubridate_1.7.4     rms_5.1-4           webshot_0.5.2      
#>  [7] RColorBrewer_1.1-2  httr_1.4.1          numDeriv_2016.8-1.1
#> [10] tools_3.6.1         backports_1.1.5     R6_2.4.1           
#> [13] rpart_4.1-15        Hmisc_4.3-1         DBI_1.1.0          
#> [16] mgcv_1.8-28         colorspace_1.4-1    nnet_7.3-13        
#> [19] withr_2.1.2         gridExtra_2.3       tidyselect_1.0.0   
#> [22] compiler_3.6.1      quantreg_5.54       cli_2.0.2          
#> [25] rvest_0.3.5         htmlTable_1.13.3    SparseM_1.78       
#> [28] xml2_1.2.5          sandwich_2.5-1      labeling_0.3       
#> [31] checkmate_2.0.0     scales_1.1.0        mvtnorm_1.1-0      
#> [34] polspline_1.1.17    digest_0.6.25       foreign_0.8-71     
#> [37] rmarkdown_2.1       base64enc_0.1-3     rticles_0.14       
#> [40] jpeg_0.1-8.1        pkgconfig_2.0.3     htmltools_0.4.0    
#> [43] dbplyr_1.4.2        htmlwidgets_1.5.1   rlang_0.4.5        
#> [46] readxl_1.3.1        rstudioapi_0.11     VGAM_1.1-2         
#> [49] farver_2.0.3        shape_1.4.4         generics_0.0.2     
#> [52] zoo_1.8-7           jsonlite_1.6.1      acepack_1.4.1      
#> [55] Formula_1.2-3       Rcpp_1.0.4          munsell_0.5.0      
#> [58] fansi_0.4.1         lifecycle_0.2.0     multcomp_1.4-12    
#> [61] stringi_1.4.6       yaml_2.2.1          MASS_7.3-51.4      
#> [64] plyr_1.8.6          ggstance_0.3.3      grid_3.6.1         
#> [67] crayon_1.3.4        lattice_0.20-38     haven_2.2.0        
#> [70] hms_0.5.3           timereg_1.9.4       knitr_1.28         
#> [73] pillar_1.4.3        codetools_0.2-16    stats4_3.6.1       
#> [76] reprex_0.3.0        glue_1.3.1          evaluate_0.14      
#> [79] latticeExtra_0.6-29 modelr_0.1.6        vctrs_0.2.4        
#> [82] png_0.1-7           foreach_1.4.8       MatrixModels_0.4-1 
#> [85] cellranger_1.1.0    gtable_0.3.0        assertthat_0.2.1   
#> [88] xfun_0.12           viridisLite_0.3.0   iterators_1.0.12   
#> [91] cluster_2.1.0       lava_1.6.7          TH.data_1.0-10
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    master C:/Users/jesse/Documents/gits/cbpaper
#> Remote:   master @ origin (https://github.com/Jesse-Islam/cbpaper.git)
#> Head:     [5f22217] 2020-03-26: AddedBrier
\end{CodeOutput}
\end{CodeChunk}

>>>>

{\centering \includegraphics{../figures/coefplots-1}

\caption{\label{fig:cs3FinalBrier} A lollipop plot demonstrating the estimated coefficients between the following three models: Cox (blue), penalized Cox (Green), penalized logisitic (red). If a coefficient is estimated to be 0, it is removed from the plot}\label{fig:coefplots}
\end{figure}
\end{CodeChunk}

@@

This report was generated on 2020-04-09 13:28:46 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 3.6.3 (2020-02-29)
#> Platform: x86_64-w64-mingw32/x64 (64-bit)
#> Running under: Windows 10 x64 (build 18363)
#> 
#> Matrix products: default
#> 
#> locale:
#> [1] LC_COLLATE=English_United States.1252 
#> [2] LC_CTYPE=English_United States.1252   
#> [3] LC_MONETARY=English_United States.1252
#> [4] LC_NUMERIC=C                          
#> [5] LC_TIME=English_United States.1252    
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.5.5               dotwhisker_0.5.0         
#>  [3] prodlim_2019.11.13        riskRegression_2020.03.27
#>  [5] pracma_2.2.9              kableExtra_1.1.0         
#>  [7] data.table_1.12.8         glmnet_3.0-2             
#>  [9] Matrix_1.2-18             casebase_0.2.1.9001      
#> [11] survival_3.1-11           magrittr_1.5             
#> [13] forcats_0.5.0             stringr_1.4.0            
#> [15] dplyr_0.8.5               purrr_0.3.3              
#> [17] readr_1.3.1               tidyr_1.0.2              
#> [19] tibble_3.0.0              ggplot2_3.3.0            
#> [21] tidyverse_1.3.0          
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-2          colorspace_1.4-1   
#>  [4] ellipsis_0.3.0      ggstance_0.3.4      htmlTable_1.13.3   
#>  [7] base64enc_0.1-3     fs_1.4.1            rstudioapi_0.11    
#> [10] farver_2.0.3        MatrixModels_0.4-1  fansi_0.4.1        
#> [13] mvtnorm_1.1-0       lubridate_1.7.8     xml2_1.3.1         
#> [16] codetools_0.2-16    knitr_1.28          Formula_1.2-3      
#> [19] jsonlite_1.6.1      cluster_2.1.0       dbplyr_1.4.2       
#> [22] png_0.1-7           compiler_3.6.3      httr_1.4.1         
#> [25] backports_1.1.6     assertthat_0.2.1    cli_2.0.2          
#> [28] acepack_1.4.1       htmltools_0.4.0     quantreg_5.55      
#> [31] tools_3.6.3         gtable_0.3.0        glue_1.4.0         
#> [34] Rcpp_1.0.4.6        cellranger_1.1.0    vctrs_0.2.4        
#> [37] nlme_3.1-145        iterators_1.0.12    xfun_0.12          
#> [40] rvest_0.3.5         lifecycle_0.2.0     polspline_1.1.17   
#> [43] MASS_7.3-51.5       zoo_1.8-7           scales_1.1.0       
#> [46] hms_0.5.3           sandwich_2.5-1      SparseM_1.78       
#> [49] RColorBrewer_1.1-2  rticles_0.14        yaml_2.2.1         
#> [52] gridExtra_2.3       rms_5.1-4           rpart_4.1-15       
#> [55] latticeExtra_0.6-29 stringi_1.4.6       foreach_1.5.0      
#> [58] checkmate_2.0.0     lava_1.6.7          shape_1.4.4        
#> [61] mets_1.2.7.1        rlang_0.4.5         pkgconfig_2.0.3    
#> [64] evaluate_0.14       lattice_0.20-41     htmlwidgets_1.5.1  
#> [67] labeling_0.3        cmprsk_2.2-9        tidyselect_1.0.0   
#> [70] plyr_1.8.6          R6_2.4.1            generics_0.0.2     
#> [73] Hmisc_4.4-0         multcomp_1.4-13     DBI_1.1.0          
#> [76] pillar_1.4.3        haven_2.2.0         foreign_0.8-76     
#> [79] withr_2.1.2         mgcv_1.8-31         nnet_7.3-13        
#> [82] modelr_0.1.6        crayon_1.3.4        rmarkdown_2.1      
#> [85] timereg_1.9.4       jpeg_0.1-8.1        grid_3.6.3         
#> [88] readxl_1.3.1        reprex_0.3.0        digest_0.6.25      
#> [91] webshot_0.5.2       numDeriv_2016.8-1.1 stats4_3.6.3       
#> [94] munsell_0.5.0       viridisLite_0.3.0
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    master C:/Users/jesse/Documents/gits/cbpaper
#> Remote:   master @ origin (https://github.com/Jesse-Islam/cbpaper.git)
#> Head:     [b31e195] 2020-03-31: Fixed penal. on time and Brier
\end{CodeOutput}
\end{CodeChunk}
